\begin{longtblr}
{
colspec={XXXXX},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S67. Patterns of pairwise differences at the focal 72kb \textit{MUC19} region between the \textit{Denisovan-like} haplotypes in 1000 Genomes Project and the archaic individuals} \newline The mean ($\mu$), standard deviation ($\sigma$), standard error of the mean (\textit{SEM}), and 95\% confidence intervals ($\pm CI_{95\%}$) of the number of pairwise distance distribution for the focal 72kb \textit{MUC19} region between the 287 \textit{Denisovan-like} haplotypes in 1000 Genomes Project and the four high-coverage archaic individuals. For the Denisovan and Altai Neanderthal, we compute the number of pairwise differences between a modern human haplotype and the two unphased archaic chromosomes, and for the Chagyrskaya and Vindija Neanderthals, we compute the number of pairwise differences between a modern human haplotype and a phased archaic haplotype.},
}
Archaic & Focal 72kb Region Pairwise Diffs. $\left( \mu\right)$ & Focal 72kb Region Pairwise Diffs. $\left( \sigma \right)$ & Focal 72kb Region Pairwise Diffs. $\left( SEM \right)$ & Focal 72kb Region Pairwise Diffs. $\left( \pm CI_{95\%} \right)$ \\
Denisovan & 49.01 & 1.994 & 0.118 & 0.232 \\
Altai Nean. & 179.838 & 2.503 & 0.148 & 0.291 \\
Chagyrskaya Nean. Hap. 1 & 170.338 & 2.457 & 0.145 & 0.286 \\
Chagyrskaya Nean. Hap. 2 & 7.547 & 2.84 & 0.168 & 0.331 \\
Vindija Nean. Hap. 1 & 170.899 & 2.179 & 0.129 & 0.254 \\
Vindija Nean. Hap. 2 & 6.108 & 2.612 & 0.154 & 0.304 \\
\end{longtblr}
