\begin{longtblr}
{
colspec={XXXXXXXXX},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S44. The average number of heterozygous sites in the focal 72kb \textit{MUC19} region among African individuals and individuals carrying a \textit{Denisovan-like} haplotype in the 1000 Genomes Project.} \newline The average number of heterozygous observed in the focal 72kb \textit{MUC19} region for each focal group in the 1000 Genomes Project: all African individuals ($n = 504$), individuals harboring one \textit{Denisovan-like} haplotype ($n = 255$), and individuals harboring two \textit{Denisovan-like} haplotypes ($n = 16$). For each group, the mean ($\mu$), standard deviation ($\sigma$), standard error of the mean (\textit{SEM}), and 95\% confidence intervals ($\pm CI_{95\%}$) of the average number of heterozygous sites genomic background distribution used to compute the \textit{P-value} are also reported. For the African individuals and individuals harboring one \textit{Denisovan-like} haplotype groups, the \textit{P-value} represents the proportion of non-overlapping 72kb windows of comparable effective sequence length where the average number of heterozygous sites is greater than or equal to that observed at the focal 72kb region. For the individuals harboring two \textit{Denisovan-like} haplotypes group, the \textit{P-value} represents the proportion of non-overlapping 72kb windows of comparable effective sequence length where the average number of heterozygous sites is less than or equal to that observed at the focal 72kb region. A \textit{P-value} less than 0.05 is considered statistically significant.},
}
Group & Focal 72kb Region (Average Number of Het. Sites) & Non-overlapping Windows $\left( \mu \right)$ & Non-overlapping Windows $\left( \sigma \right)$ & Non-overlapping Windows $\left( SEM \right)$ & Non-overlapping Windows $\left( \pm CI_{95\%} \right)$ & $P-value$ \\
African Inds. & 75.315 & 73.319 & 25.708 & 0.144 & 0.283 & 0.424 \\
Inds. with One $Denisovan-like$ Hap. & 287.341 & 54.639 & 23.128 & 0.13 & 0.255 & $3.157e^{-5}$ \\
Inds. with Two $Denisovan-like$ Haps. & 4.188 & 52.579 & 24.891 & 0.14 & 0.274 & $6.945e^{-4}$ \\
\end{longtblr}
