\begin{longtblr}
{
colspec={XXXXXXXX},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S36. Sequence divergence from the Denisovan for the Altai Neanderthal and all African Individuals in the 1000 Genomes Project (1KG) at the focal 72kb \textit{MUC19} region.} \newline The observed sequence divergence from the Densisovan for the Altai Neanderthal (i.e., the number of pairwise differences between the Altai Neanderthal's and Denisovan's unphased genotypes normalized by the effective sequence length) and all Africans in the 1KG (i.e., the average number of pairwise differences between all African haplotypes in the 1KG and the Denisovan's unphased genotypes normalized by the effective sequence length). For each comparison to the Denisovan, the mean ($\mu$), standard deviation ($\sigma$), standard error of the mean (\textit{SEM}), and 95\% confidence intervals ($\pm CI_{95\%}$) of the sequence divergence genomic background distribution used to compute the \textit{P-value} are also reported. The \textit{P-value} represents the proportion of non-overlapping 72kb windows of comparable effective sequence length where the sequence divergence is greater than or equal to that observed at the focal 72kb region. A \textit{P-value} less than 0.05 is considered statistically significant. Note that at the focal 72kb region, the effective sequence length with respect to the Denisovan is 46136bp and 48435bp for the Altai Neanderthal and African comparison, respectively.},
}
Comparison & Focal 72kb Region (Pairwise Diffs.) & Focal 72kb Region (Seq. Div.) & 72kb Nonoverlapping Windows $\left( \mu \right)$ & 72kb Nonoverlapping Windows $\left( \sigma \right)$ & 72kb Nonoverlapping Windows $\left( SEM \right)$ & 72kb Nonoverlapping Windows $\left( \pm CI_{95\%} \right)$ & $P-value$ \\
Altai Nean. & 174.5 & 0.003782 & 0.001 & $6.013e^{-4}$ & $3.501e^{-6}$ & $6.862e^{-6}$ & 0.002 \\
AFR & 194.885 & 0.004024 & 0.001 & $5.529e^{-4}$ & $3.168e^{-6}$ & $6.210e^{-6}$ & 0.002 \\
\end{longtblr}
