\begin{longtblr}
{
colspec={XXXXXXXXX},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S43. The number of heterozygous sites in the focal 72kb \textit{MUC19} region among archaic individuals.} \newline The number of heterozygous observed in the focal 72kb \textit{MUC19} region for each of the high-coverage archaic individuals. For each archaic individual, the mean ($\mu$), standard deviation ($\sigma$), standard error of the mean (\textit{SEM}), and 95\% confidence intervals ($\pm CI_{95\%}$) of the heterozygous sites genomic background distribution used to compute the \textit{P-value} are also reported. The \textit{P-value} represents the proportion of non-overlapping 72kb windows of comparable effective sequence length where the number of heterozygous sites is greater than or equal to that observed at the focal 72kb region. A \textit{P-value} less than 0.05 is considered statistically significant.},
}
Archaic & Focal 72kb Region (Het. Sites) & Non-overlapping Windows $\left( \mu \right)$ & Non-overlapping Windows $\left( \sigma \right)$ & Non-overlapping Windows $\left( SEM \right)$ & Non-overlapping Windows $\left( \pm CI_{95\%} \right)$ & $P-value$ \\
Denisovan & 6 & 8.747 & 14.169 & 0.081 & 0.159 & 0.455 \\
Altai Nean. & 1 & 7.862 & 15.261 & 0.087 & 0.171 & 0.679 \\
Chagyrskaya Nean. & 168 & 6.534 & 13.242 & 0.076 & 0.149 & $2.307e^{-4}$ \\
Vindija Nean. & 171 & 7.837 & 13.598 & 0.078 & 0.153 & $3.282e^{-4}$ \\
\end{longtblr}
