\begin{longtblr}
{
colspec={p{2cm}XXXXp{2cm}p{2cm}p{2cm}p{2cm}p{1cm}p{1cm}X},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S37. Sequence divergence between the \textit{Denisovan-like} haplotype in MXL and unphased archaic individuals at the focal 72kb \textit{MUC19} region.} \newline The observed sequence divergence---i.e., the number of pairwise differences between a modern human haplotype and an archaic genotype normalized by the effective sequence length---between the \textit{Denisovan-like} haplotype in the focal MXL individual (i.e., NA19664), who harbors two \textit{Denisovan-like} haplotypes and has no heterozygous sites at the focal 72kb region, and the four unphased high-coverage archaic individuals. For each archaic individual, the mean ($\mu$), standard deviation ($\sigma$), standard error of the mean (\textit{SEM}), and 95\% confidence intervals ($\pm CI_{95\%}$) of the sequence divergence genomic background distribution used to compute the \textit{P-value} are also reported. The \textit{P-value} represents the proportion of non-overlapping 72kb windows of comparable effective sequence length where the sequence divergence is less than or equal to that observed at the focal 72kb region. After correcting for two multiple comparisons---i.e., one per haplotype---a \textit{P-value} less than 0.025 is considered statistically significant. Note that at the focal 72kb region, the effective sequence length with respect to the NA19664 individual is 48435bp, 48654bp, 48121bp, and 48447bp for the Denisovan, Altai Neanderthal, Chagyrskaya Neanderthal, and Vindija Neanderthal, respectively.},
}
Archaic & Focal 72kb Region (Pairwise Diffs. Hap. 1) & Focal 72kb Region (Pairwise Diffs. Hap. 2) & Focal 72kb Region (Seq. Div. Hap. 1) & Focal 72kb Region (Seq. Div. Hap. 2) & 72kb Non-overlapping Windows $\left( \mu \right)$ & 72kb Non-overlapping Windows $\left( \sigma \right)$ & 72kb Non-overlapping Windows $\left( SEM \right)$ & 72kb Non-overlapping Windows $\left( \pm CI_{95\%} \right)$ & $P-value$ (Hap. 1) & $P-value$ (Hap. 2) \\
Denisovan & 47 & 47 & 0.00097 & 0.00097 & 0.001 & $6.132e^{-4}$ & $2.484e^{-6}$ & $4.870e^{-6}$ & 0.237 & 0.237 \\
Altai Nean. & 177.5 & 177.5 & 0.003648 & 0.003648 & 0.001 & $6.028e^{-4}$ & $2.442e^{-6}$ & $4.787e^{-6}$ & 0.995 & 0.995 \\
Chagyrskaya Nean. & 87.5 & 87.5 & 0.001818 & 0.001818 & 0.001 & $6.074e^{-4}$ & $2.465e^{-6}$ & $4.832e^{-6}$ & 0.811 & 0.811 \\
Vindija Nean. & 88 & 88 & 0.001816 & 0.001816 & 0.001 & $6.041e^{-4}$ & $2.447e^{-6}$ & $4.796e^{-6}$ & 0.806 & 0.806 \\
\end{longtblr}
