\begin{longtblr}
{
colspec={XXXXXXX},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S10. $\boldsymbol{PBS_{A:CHB:CEU}}$ values for the focal 742kb \textit{MUC19} region among different Indigenous American ancestry (IAA) demes in MXL.} \newline The $PBS_{A:CHB:CEU}$ values observed in the focal 742kb region for different IAA-partitioned demes in MXL: all individuals in the MXL population ($n = 64$; \textit{A} = All MXL Individuals), MXL individuals with genome-wide IAA $> 50\%$ ($n = 27$; \textit{A} = MXL Individuals $> 50\%$ IAA), and MXL individuals with genome-wide IAA $< 50\%$ ($n = 37$; \textit{A} = MXL Individuals $< 50\%$ IAA). The $PBS_{A:CHB:CEU}$ statistic uses the logarithmic transformation of pairwise $F_{ST}$ estimates to measure the branch length in deme \textit{A} since its divergence from the two control populations: CHB and CEU. For each IAA-partitioned deme, the mean ($\mu$), standard deviation ($\sigma$), standard error of the mean (\textit{SEM}), and 95\% confidence intervals ($\pm CI_{95\%}$) of the $PBS_{A:CHB:CEU}$  genomic background distribution used to compute the \textit{P-value} are also reported. The \textit{P-value} represents the proportion of non-overlapping 742kb windows of comparable effective sequence length where the $PBS_{A:CHB:CEU}$ value is greater than or equal to that observed at the focal 742kb region. A \textit{P-value} less than 0.05 is considered statistically significant.},
}
$PBS_{A:CHB:CEU}$ & Focal 742kb Region $\left( PBS \right)$ & 742kb Non-overlapping Windows $\left( \mu \right)$ & 742kb Non-overlapping Windows $\left( \sigma \right)$ & 742kb Non-overlapping Windows $\left( SEM \right)$ & 742kb Non-overlapping Windows $\left( \pm CI_{95\%} \right)$ & $P-value$ \\
$A =$ All MXL Inds. & 0.066 & 0.005 & 0.011 & $1.949e^{-4}$ & $3.822e^{-4}$ & 0.004 \\
$A =$ MXL Inds. $>50\%$ IAA & 0.133 & 0.018 & 0.024 & $4.128e^{-4}$ & $8.093e^{-4}$ & 0.003 \\
$A =$ MXL Inds. $<50\%$ IAA & 0.029 & 0.002 & 0.007 & $1.231e^{-4}$ & $2.414e^{-4}$ & 0.01 \\
\end{longtblr}
