\begin{longtblr}
{
colspec={XXXX},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S56. Demographic model from Medina-Mu\~{n}oz et al., 2023 with archaic introgression.} \newline Demographic parameters used for \textit{PBS} simulations.},
}
Parameter & Value & Description & Reference \\
Population size & 13580 & Ancestral Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Population size & 13249 & Archaic Pop. size & Jacobs et al., 2019; Malaspinas et al., 2016 \\
Population size & 27142 & AMH Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Population size & 826 & NEA Pop. size & Jacobs et al., 2019; Malaspinas et al., 2016 \\
Population size & 5083 & DEN Pop. size & Jacobs et al., 2019; Malaspinas et al., 2016 \\
Population size & 1835 & OOA Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Population size & 27142 & AFR Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Population size & 2761 & EUR Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Population size & 1955 & EAS Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Population size & 1313 & MXB Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Population size & 20000 & MXL Pop. size & Medina-Mu\~{n}oz et al., 2023 \\
Growth rate per generation & 0.001 & EUR Pop. growth rate & Medina-Mu\~{n}oz et al., 2023 \\
Growth rate per generation & 0.001 & EAS Pop. growth rate & Medina-Mu\~{n}oz et al., 2023 \\
Growth rate per generation & 0.003 & MXB Pop. growth rate & Medina-Mu\~{n}oz et al., 2023 \\
Migration rate per generation & $1.586e^{-4}$ & AFR-OOA migration rate & Medina-Mu\~{n}oz et al., 2023 \\
Migration rate per generation & $2.502e^{-5}$ & AFR-EUR migration rate & Medina-Mu\~{n}oz et al., 2023 \\
Migration rate per generation & $3.295e^{-6}$ & AFR-EAS migration rate & Medina-Mu\~{n}oz et al., 2023 \\
Migration rate per generation & $6.624e^{-5}$ & EUR-EAS migration rate & Medina-Mu\~{n}oz et al., 2023 \\
Migration rate per generation & 0.05 & MXB-MXL migration rate & Medina-Mu\~{n}oz et al., 2023 \\
Migration rate per generation & 0.058 & EUR-MXL migration rate & Medina-Mu\~{n}oz et al., 2023 \\
Admixture percentage & 0.05 & NEA admixture into OOA & Green et al., 2010 \\
Admixture percentage & 0.05 & DEN admixture into EAS & Skoglund and Jakobsson 2011 \\
Admixture percentage & 0.112 & AFR admixture into MXL & Medina-Mu\~{n}oz et al., 2023 \\
Admixture percentage & 0.007 & EAS admixture into MXL & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 20225 & Ancestral-Archaic split & Jacobs et al., 2019; Malaspinas et al., 2016 \\
Epoch time (g. a.) & 16671 & Ancestral-AMH split & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 15090 & Archaic-DEN split & Jacobs et al., 2019; Malaspinas et al., 2016 \\
Epoch time (g. a.) & 15090 & Archaic-NEA split & Jacobs et al., 2019; Malaspinas et al., 2016 \\
Epoch time (g. a.) & 3046 & AMH-OoA split & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 3046 & AMH-AFR split & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 2069 & NEA admixture into OOA & Green et al., 2010; Pr\"{u}fer et al., 2014; Pr\"{u}fer et al., 2017 \\
Epoch time (g. a.) & 1764 & OOA-EUR split & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 1764 & OOA-EAS split & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 1552 & DEN admixture into EAS & Reich et al., 2011 \\
Epoch time (g. a.) & 1123 & EAS-MXB split & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 16 & MXL divergence from EUR and MXB & Medina-Mu\~{n}oz et al., 2023 \\
Epoch time (g. a.) & 13 & AFR and EAS admixture into MXL & Medina-Mu\~{n}oz et al., 2023 \\
Mutation rate & $1.315e^{-8}$ & Per-base per-generation mutation rate & Hubisz and Siepel 2020 \\
Uniform recombination rate & $6.000e^{-9}$ & Per-base per-generation recombination rate & Hinch et al., 2011 \\
MXL sample size & 64 & MXL sample size & Based on the number of individuals in MXL from 1000 Genomes Project \\
EAS sample size & 103 & EAS sample size & Based on the number of individuals in CHB from 1000 Genomes Project \\
EUR sample size & 99 & EUR sample size & Based on the number of individuals in CEU from 1000 Genomes Project \\
Generation time & 29 & Number of years per generation & Fenner 2005 \\
\end{longtblr}
