\begin{longtblr}
{
colspec={XXXXXXXXXp{1.55cm}XXX},
hlines={solid, 1pt},
vlines={solid, 1pt},
cells={halign=c, valign=m},
width=\linewidth,
rowhead=1,
row{odd}={Grey},
row{1}={Brown, fg=white, halign=c, valign=m},
caption={\textbf{Table S19. Comparisons of the distributions of repeat copies between different focal groups among all individuals in the 1000 Genome Project.} \newline Comparing the distributions of repeat copy numbers between focal groups: individuals with at least one introgressed tract overlapping the repeat region vs individuals with no introgressed tracts overlapping the repeat region and admixed American vs non-admixed American individuals. For each comparison, the total number of individuals, the number of individuals with elevated repeat copies (i.e., those with $> 487$ repeat copies), the proportion of individuals with elevated repeat copies per population, and the results of the Proportions \textit{Z}-Test, and Mann-Whitney \textit{U}-Test is reported. A \textit{P-value} less than 0.05 is considered statistically significant.},
}
Group 1 & Group 2 & Number of Inds. (Group 1) & Number of Inds. (Group 2) & Number of Inds. with Elevated Repeats (Group 1) & Number of Inds. with Elevated Repeats (Group 2) & Prop. of Inds. with Elevated Repeats (Group 1) & Prop. of Inds. with Elevated Repeats (Group 2) & $Z-Statistic$ & $P-value$ (Prop. $Z$-Test) & $U-Statistic$ & $P-value$ (Mann-Whitney $U$-Test) \\
All Inds.: $\geq 1$ Overlapping Tract & All Inds.: No Overlapping Tract & 185 & 2162 & 102 & 16 & 0.551 & 0.007 & 32.496 & $6.015e^{-232}$ & 375108.5 & $1.597e^{-87}$ \\
All AMR Inds. & All non-AMR Inds. & 347 & 2000 & 91 & 27 & 0.262 & 0.013 & 19.575 & $1.266e^{-85}$ & 445495 & $1.424e^{-17}$ \\
\end{longtblr}
